Capstone Movielens Report

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_SmoothedDay_effect`.

Builds the *User+Movie+Genre+Year+SmoothedDay Effect (hereafter UMGYDE for short) Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

@@

@@

@@

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

@@

The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
```

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

@@

@@

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.

@@

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

>>>>

Builds the *User+Movie+Genre+Year+SmoothedDay Effect* (hereafter *UMGYDE* for short) *Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

@@

```{r eval=FALSE}
  lss.UMGYD_effect <- edx |> 
    train_UMGY_SmoothedDay_effect(lss.best_degree, lss.best_span)
```
:::

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);

@@

Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.calc_UMGY_SmoothedDay_effect.args.degree) and [span](#func.calc_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
:::

@@

The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect <- function(train_set, 
                                          degree = NA, 
                                          span = NA,
                                          lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_SmoothedDay_effect
`lambda` is `NA`")
  }

  train_set |> 
    calc_day_general_effect(lambda) |>
    calc_UMGY_SmoothedDay_effect(degree, span)
}
```

@@

Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.

@@

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.

@@

The *MSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.

@@

The *RMSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
:::

@@

Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
